---
title: "DEA_Zac"
author: "Zachariah Alex"
date: "2022-10-31"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
tab <- matrix(c("Facility 1","Facility 2","Facility 3","Facility 4","Facility 5","Facility 6",
150,400,320,520,350,320,
0.2,0.7,1.2,2.0,1.2,0.7,
14000,14000,42000,28000,19000,14000,
3500,21000,10500,42000,25000,15000), ncol=5, byrow=F)
colnames(tab) <- c('DMU', 'Staff Hours per Day','Supplies per Day','Reimbursed Patient-Days','Privately Paid Patient-Days')

tab <- as.table(tab)
tab
```

```{r}

library(Benchmarking)

```

```{r}
x<-matrix(c(150,400,320,520,350,320,
0.2,0.7,1.2,2.0,1.2,0.7),ncol=2)
y<-matrix(c(14000,14000,42000,28000,19000,14000,
3500,21000,10500,42000,25000,15000),ncol=2)

colnames(y)<-c("Reimbursed Patient-Days","Privately Paid Patient-Days")
colnames(x)<-c("Staff Hours per Day","Supplies per Day")
```


```{r}
DEA_fdh<-dea(x,y,RTS = "fdh")
DEA_fdh

peers(DEA_fdh)
lambda(DEA_fdh)

tab_DEA_fdh <- matrix(c("Facility 1","Facility 2","Facility 3","Facility 4","Facility 5","Facility 6",
                1,1,1,1,1,1,
                1,1,1,1,1,1,
                1,2,3,4,5,6
                ),ncol=4)
colnames(tab_DEA_fdh) <- c('DMU', 'e','lambda','peers')
tab_DEA_fdh
```

```{r}
DEA_crs<-dea(x,y,RTS = "crs")
DEA_crs

peers(DEA_crs)
lambda(DEA_crs)


tab_DEA_crs <- matrix(c("Facility 1","Facility 2","Facility 3","Facility 4","Facility 5","Facility 6",
                1,1,1,1,0.9775,0.8675,
                1,1,1,1,"0.2 0.08 0 0.53",1,
                1,2,3,4,"1 2 4","1 2 4"
                ),ncol=4)
colnames(tab_DEA_crs) <- c('DMU', 'e','lambda','peers')
tab_DEA_crs
```


```{r}
DEA_vrs<-dea(x,y,RTS = "vrs")
DEA_vrs

peers(DEA_vrs)
lambda(DEA_vrs)

tab_DEA_crs <- matrix(c("Facility 1","Facility 2","Facility 3","Facility 4","Facility 5","Facility 6",
                1,1,1,1,1,0.8963,
                1,1,1,1,1,"0.401 0.342 0 0 0.256",
                1,2,3,4,5,"1 2 5"
                ),ncol=4)
colnames(tab_DEA_crs) <- c('DMU', 'e','lambda','peers')
tab_DEA_crs
```
```{r}
DEA_irs<-dea(x,y,RTS = "irs")
DEA_irs
peers(DEA_irs)
lambda(DEA_irs)

tab_DEA_irs <- matrix(c("Facility 1","Facility 2","Facility 3","Facility 4","Facility 5","Facility 6",
                1,1,1,1,1,0.8963,
                1,1,1,1,1,"0.401 0.342 0 0 0.256",
                1,2,3,4,5,"1 2 5"
                ),ncol=4)
colnames(tab_DEA_irs) <- c('DMU', 'e','lambda','peers')
tab_DEA_irs
```

```{r}
DEA_drs<-dea(x,y,RTS = "drs")
DEA_drs
peers(DEA_drs)
lambda(DEA_drs)

tab_DEA_drs <- matrix(c("Facility 1","Facility 2","Facility 3","Facility 4","Facility 5","Facility 6",
                1,1,1,1,0.9775,0.8675,
                1,1,1,1,"0.2 0.08 0 0.53","0.342 0.3949 0 0.1310",
                1,2,3,4,"1 2 4","1 2 4"
                ),ncol=4)
colnames(tab_DEA_drs) <- c('DMU', 'e','lambda','peers')
tab_DEA_drs
```
```{r}
DEA_frh<-dea(x,y,RTS = "add")
DEA_frh
peers(DEA_frh)
lambda(DEA_frh)

tab_DEA_frh <- matrix(c("Facility 1","Facility 2","Facility 3","Facility 4","Facility 5","Facility 6",
                1,1,1,1,1,1,
                1,1,1,1,1,1,
                1,2,3,4,5,6
                ),ncol=4)
colnames(tab_DEA_frh) <- c('DMU', 'e','lambda','peers')
tab_DEA_frh
```
#INTERPRETATION OF ALL THE ABOVE RESULTS

# 1 - From fdh assumption ,we can see that Facilities 1,2,3,4,5,6 are 100 % efficient
#     The Free Disposability Hull (FDH) is a no convexity assumption. 
#     It follows a non-parametric method to measure the efficiency of the DMUs.



# 2 - From the crs assumption we made, we can see that Facilities 1,2,3,4 are 100% efficient
#     Facility 5 and Facility 6 are only 97.75% and 86.75% efficient respectively
#     Nearest neighbour for Facility 5 and Facility 6 are Facility 1,Facility 2 and Facility 4
#     In this case Facilities 1, 2, 3 and 4 can be scaled up

# 3 - From the vrs assumption we made, we can see that Facilities 1,2,3,4,5 are 100% efficient
#     Facility 6 is only 89.63% efficient
#     Nearest neighbour for Facility 6 are Facility 1,Facility 2 and Facility 5
#     Facility 1, 2 and 5 have weights of 0.4, 0.34 and 0.26 respectively


# 4 - From the irs assumption we made, we can see that Facilities 1,2,3,4,5 are 100% efficient
#     Facility 6 is only 89.63% efficient
#     Nearest neighbour for Facility 6 are Facility 1,Facility 2 and Facility 5

# 5 - From the drs assumption we made, we can see that Facilities 1,2,3,4 are 100% efficient 
#     Facility 5 and Facility 6 are only 97.75% and 86.75% efficient respectively
#     Nearest neighbour for Facility 5 and Facility 6 are Facility 1,Facility 2 and Facility 4 
#     Peer units are 1, 2 and 4 with weights of 0.34, 0.4 and 0.13 respectively
#     Facilities 5 & 6 can be scaled down


# 6 - From the frh assumption we made,we can see that Facilities 1,2,3,4,5,6 are 100 % efficient
#     The Free Replicability Hull (FRH) is a no convexity assumption like FDH
#     It follows a non-parametric method to measure the efficiency of the DMUs